One Year HPC Certification Forum in Retrospective

### 2019-04-26 paper.tex
Reviewer 3 typos fixed.

There is a generally accepted set of skills and competencies necessary to efficiently use HPC resources.
This skill set depends on the role and domain of the practitioner but also on the available infrastructure of the centre providing the computing resources.
For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., Slurm.
Now rather than providing that scientists with a list of instructions to be followed in a copy and paste fashion or a never-ending list of things they should know, we want them to understand each of the required steps without having to learner everything about it, but at the same time understand how it fits into the bigger picture of using an HPC system.
For instance, understanding Slurm is a good example of a very fine-grained skill that fits under a more generic skill defined as "resource management", illustrating concepts across the rich variety of available resource managers.

@@

As the tree serves the purpose of organising the skills, the references from one branch to a skill in another branch are allowed.
This import feature makes the reuse of the skill definitions possible, at the same time allowing users to navigate the tree according to the semantics.

@@

The learning outcomes of this skill, marked with B to indicate its basic level, are focusing on the most fundamental knowledge required to use Slurm effectively.
An intermediate version of the skill could, for example, could cover how to create reservations or special queues.

@@

If the user didn't meet the pass criteria, they will be informed about their score.
The user can then retry to obtain the certificate after a cool-down period (typically one week), but not immediately afterwards to prevent success via brute force methods.
To enforce this, the information about when the exam was undertaken is linked to the user's name and email.
As the sole purpose of the multiple choice questions is the examination, the incorrectly answered questions will not revealed.
We assume that high quality training materials available within the HPC community, and covering the individual skills being part of this certification program, offer constructive feedback and other ways of consolidating the newly acquired knowledge.
Therefore, the Forum's only concern is to provide the mechanism of certifying whether the learners posses that knowledge or not;
As opposed to pointing out gaps in their understanding.

@@

The text file a contains the same information, as well as a verification URL that can be given to a third-party to confirm the certificate's credibility.
It is also PGP signed using the private key of the HPC Certification Forum to allow verification with the public key. An example file looks as follows:
\begin{verbatim}
-----BEGIN PGP SIGNED MESSAGE-----
Hash: SHA512
HPC Certification Forum Certificate
This text confirms that "Julian M. Kunkel" has
successfully obtained the certificate
"HPC driving license" (id: 1) at 02/2019.
Verification URL: https://hpc-certification.org/[...]
-----BEGIN PGP SIGNATURE-----
[...]
-----END PGP SIGNATURE-----
\end{verbatim}

@@

The program brings multiple benefits to everyone involved in HPC teaching and training. It's obvious that making clear what skills are required or recommended for a competent HPC user would be helpful to both the HPC service providers and practitioners. Training providers could bundle together skills that are most beneficial for specific user roles and scientific domains, which would allow practitioners to browse through skills to quickly identify and learn the skills required to perform their tasks. The variety of training offered within our community makes finding the right resources more complicated than it should be -- the certification program will provide useful information where the desired skills could be learnt. The examination confirming that a certain set of competencies has been acquired makes the learning process more complete and meaningful.

>>>>

There is a generally accepted set of skills and competencies necessary to efficiently use HPC resources.
This skill set depends on the role and domain of the practitioner but also on the available infrastructure of the centre providing the computing resources.
For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., Slurm.
Now rather than providing that scientists with a list of instructions to be followed in a copy and paste fashion or a never-ending list of things they should know, we want them to understand each of the required steps without having to learn everything about it, but at the same time understand how it fits into the bigger picture of using an HPC system.
For instance, understanding Slurm is a good example of a very fine-grained skill that fits under a more generic skill defined as "resource management", illustrating concepts across the rich variety of available resource managers.

@@

As the tree serves the purpose of organising the skills, the references from one branch to a skill in another branch are allowed.
This important feature makes the reuse of the skill definitions possible, at the same time allowing users to navigate the tree according to the semantics.

@@

The learning outcomes of this skill, marked with B to indicate its basic level, are focusing on the most fundamental knowledge required to use Slurm effectively.
An intermediate version of the skill could, for example, cover how to create reservations or special queues.

@@

If the user didn't meet the pass criteria, they will be informed about their score.
The user can then retry to obtain the certificate after a cool-down period (typically one week), but not immediately afterwards to prevent success via brute force methods.
To enforce this, the information about when the exam was undertaken is linked to the user's name and email.
As the sole purpose of the multiple choice questions is the examination, the incorrectly answered questions will not be revealed.
We assume that high quality training materials available within the HPC community, and covering the individual skills being part of this certification program, offer constructive feedback and other ways of consolidating the newly acquired knowledge.
Therefore, the Forum's only concern is to provide the mechanism of certifying whether the learners posses that knowledge or not;
As opposed to pointing out gaps in their understanding.

@@

The text file contains the same information, as well as a verification URL that can be given to a third-party to confirm the certificate's credibility.
It is also PGP signed using the private key of the HPC Certification Forum to allow verification with the public key. An example file looks as follows:
\begin{verbatim}
-----BEGIN PGP SIGNED MESSAGE-----
Hash: SHA512
HPC Certification Forum Certificate
This text confirms that "Julian M. Kunkel" has
successfully obtained the certificate
"HPC driving license" (id: 1) at 02/2019.
Verification URL: https://hpc-certification.org/[...]
-----BEGIN PGP SIGNATURE-----
[...]
-----END PGP SIGNATURE-----
\end{verbatim}

@@

The program brings multiple benefits to everyone involved in HPC teaching and training. It's obvious that making clear what skills are required or recommended for a competent HPC user would be helpful to both the HPC service providers and practitioners. Training providers could bundle together skills that are most beneficial for specific user roles and scientific domains, which would allow practitioners to browse through skills to quickly identify and learn the skills required to perform their tasks. The variety of training offered within our community makes finding the right resources more complicated than it should be -- the certification program will provide useful information where the desired skills could be learned. The examination confirming that a certain set of competencies has been acquired makes the learning process more complete and meaningful.
